Pulling oral and IV data from CvTdb

### 2023-05-10 invivopkfit/data-raw/pulling_oral_iv_data_cvtdb.Rmd
Add data-raw/ Rmd to put cleaned, filtered version of CvT data in data/

Save the pulled CVT data with the edits/normalizations, andf also save the current date.

>>>>

Filter out any variables that are all-NA.

```{r}
all_na <- cvt[, sapply(.SD, function(x) all(is.na(x)))]
na_vars <- names(all_na)[all_na %in% TRUE]
cvt[, (na_vars) := NULL]
```

Save the pulled CVT data with the edits/normalizations, and also save the current date.
